### 2023-01-28 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@9a4da8d988c19010dab17a231a563c4a46c68be4 🚀

The recognition of the variability of species interactions and the
emergence of numerical methods have led ecologists to rethink their
representation of ecological networks, slowly moving from a binary to a
probabilistic view of species interactions
(\textbf{Poisot2016StrProa?}). This has several benefits. For example,
probabilities represent the limit of our knowledge about species
interactions and can indicate the expected frequency of two species
interacting with each other {[}TK{]}. They are also very helpful in
predictive models when modeling the spatial distribution of species
(Cazelles \emph{et al.} 2016) and the temporal variability of ecological
networks {[}TK{]}, generating new ecological data (e.g., Strydom
\emph{et al.} 2022), and identifying priority sampling locations (see
Andrade-Pacheco \emph{et al.} 2020 for an ecological example of a
sampling optimization problem). Moreover, the high rate of false
negatives in ecological network data, resulting from the difficulty of
witnessing interactions between rare species, makes it hard to interpret
non-observations of species interactions ecologically (Catchen \emph{et
al.} 2023). Using probabilities instead of yes-no interactions accounts
for these observation errors; in that case, only forbidden interactions
(Jordano \emph{et al.} 2003; Olesen \emph{et al.} 2010) would have a
probability value of zero (but see Gonzalez-Varo \& Traveset 2016).

@@

@@

@@

>>>>

The recognition of the variability of species interactions and the
emergence of numerical methods have led ecologists to rethink their
representation of ecological networks, slowly moving from a binary to a
probabilistic view of species interactions (Poisot \emph{et al.} 2016).
This has several benefits. For example, probabilities represent the
limit of our knowledge about species interactions and can indicate the
expected frequency of two species interacting with each other {[}TK{]}.
They are also very helpful in predictive models when modeling the
spatial distribution of species (Cazelles \emph{et al.} 2016) and the
temporal variability of ecological networks {[}TK{]}, generating new
ecological data (e.g., Strydom \emph{et al.} 2022), and identifying
priority sampling locations (see Andrade-Pacheco \emph{et al.} 2020 for
an ecological example of a sampling optimization problem). Moreover, the
high rate of false negatives in ecological network data, resulting from
the difficulty of witnessing interactions between rare species, makes it
hard to interpret non-observations of species interactions ecologically
(Catchen \emph{et al.} 2023). Using probabilities instead of yes-no
interactions accounts for these observation errors; in that case, only
forbidden interactions (Jordano \emph{et al.} 2003; Olesen \emph{et al.}
2010) would have a probability value of zero (but see Gonzalez-Varo \&
Traveset 2016).

@@

\[P(i \rightarrow j)\]

@@

\[P(i \rightarrow j | C, A, N, E, t)\]

i = predator j = prey C = co-occurrence A = area N = relative abundance
E = environment (including network) t = time

@@

\leavevmode\hypertarget{ref-Poisot2016Structure}{}%
Poisot, T., Cirtwill, A.R., Cazelles, K., Gravel, D., Fortin, M.-J. \&
Stouffer, D.B. (2016). The structure of probabilistic networks.
\emph{Methods in Ecology and Evolution}, 7, 303--312.
